The SMT Competition 2015--2018

### 2019-02-01 2018/report/SMT-COMP.tex
Nicer tables (using the booktabs package)

\usepackage{jsat}
\usepackage{amsmath, amsthm, amssymb}
%\usepackage[pdf]{pstricks}
%\usepackage{pst-tree}

@@

\begin{table}
  \caption{Number of benchmarks and logics in the SMT Library}
  \label{table:smtlib}
  \centering
  \begin{tabular}{|r@{\ \ }l|r|r|r|r|}
    \hline
                               & & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    \multirow{2}{*}{Non-incremental $\{$} & benchmarks & 196375 & 196114 & 258079 & 336844 \\
                                          & logics     &     40 &     40 &     49 &     51 \\
    \multirow{2}{*}{Incremental $\{$}     & benchmarks &  10019 &  10024 &   6262 &  10167 \\
                                          & logics     &     15 &     15 &     22 &     26 \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Number of divisions in each competition track}
  \label{table:divisions}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    Main track        &  40 & 40 & 49 & 50 \\
    Application track &  14 & 14 & 16 & 21 \\
    Unsat-core track  &  -- & 40 & 41 & 44 \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Number of benchmarks used in the main track (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.82]{\begin{tabular}{|l|r|r|r|r|}
    \hline
    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \hline
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \hline
  \end{tabular}}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the application track (by
    division)}
  \label{table:benchmarks-application-track}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    Division & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    ALIA       &   24 &   24 &   24 &   24 \\
    ANIA       &    3 &    3 &    3 &    3 \\
    AUFNIRA    &   -- &   -- &   -- &  117 \\
    BV         &   -- &   -- &   -- &   17 \\
    LIA        &    6 &    6 &    6 &    6 \\
    QF\_ABV    &   -- &   -- &   -- &   15 \\
    QF\_ALIA   &   44 &   44 &   44 &   44 \\
    QF\_ANIA   &    5 &    5 &    5 &    5 \\
    QF\_AUFBV  &   -- &   -- &   -- &   10 \\
    QF\_AUFLIA &   72 &   72 &   72 &   72 \\
    QF\_BV     &   18 &   18 &   18 &  815 \\
    QF\_BVFP   &   -- &   -- &    2 &    2 \\
    QF\_FP     &   -- &   -- &    2 &    2 \\
    QF\_LIA    &   65 &   69 &   68 &   69 \\
    QF\_LRA    &   10 &   10 &   10 &   10 \\
    QF\_NIA    &   10 &   10 &   10 &   10 \\
    QF\_UFBV   &   -- &   -- &   -- & 2327 \\
    QF\_UFLIA  &  905 &  905 &  780 &  780 \\
    QF\_UFLRA  & 3331 & 3331 & 3056 & 3058 \\
    QF\_UFNIA  &    1 &    1 &    1 &    1 \\
    UFLRA      & 5358 & 5358 & 1870 & 1870 \\
    \hline
    Total      & 9852 & 9856 & 5971 & 9257 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the unsat-core track (by
    division)}
  \label{table:benchmarks-unsat-core-track}
  \centering
  \scalebox{1}[.93]{\begin{tabular}{|l|r|r|r|}
    \hline
    Division & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    ALIA       &     41 &     41 &     41 \\
    AUFBVDTLIA &     -- &     -- &     25 \\
    AUFLIA     &      3 &      3 &      3 \\
    AUFLIRA    &  19749 &  19771 &  19771 \\
    AUFNIRA    &   1046 &   1050 &   1053 \\
    BV         &     56 &     94 &   4937 \\
    LIA        &    191 &    233 &    233 \\
    LRA        &    319 &   1106 &   1539 \\
    NIA        &      3 &      4 &      4 \\
    NRA        &   3788 &   3801 &   3801 \\
    QF\_ABV    &   4644 &   4673 &   4677 \\
    QF\_ABVFP  &     -- &   3934 &   3934 \\
    QF\_ALIA   &     80 &     80 &     80 \\
    QF\_ANIA   &      8 &      8 &      8 \\
    QF\_AUFBV  &     31 &     25 &     25 \\
    QF\_AUFLIA &    516 &    516 &    516 \\
    QF\_AUFNIA &     15 &     12 &     12 \\
    QF\_AX     &    279 &    279 &    279 \\
    QF\_BV     &  17172 &  23732 &  25700 \\
    QF\_BVFP   &      6 &   3174 &   3174 \\
    QF\_DT     &     -- &     -- &   4422 \\
    QF\_FP     &  17213 &  20028 &  20026 \\
    QF\_IDL    &    816 &    816 &    816 \\
    QF\_LIA    &   2840 &   2844 &   3019 \\
    QF\_LIRA   &      5 &      5 &      5 \\
    QF\_LRA    &    633 &    671 &    683 \\
    QF\_NIA    &    316 &   3130 &   4842 \\
    QF\_NIRA   &      2 &      2 &      2 \\
    QF\_NRA    &   4948 &   5296 &   5357 \\
    QF\_RDL    &    113 &    113 &    113 \\
    QF\_UF     &   4100 &   4101 &   4330 \\
    QF\_UFBV   &     31 &     31 &    575 \\
    QF\_UFIDL  &    335 &    322 &    322 \\
    QF\_UFLIA  &    195 &    183 &    183 \\
    QF\_UFLRA  &    853 &    511 &    511 \\
    QF\_UFNIA  &      7 &      7 &      7 \\
    QF\_UFNRA  &     18 &     11 &     11 \\
    UF         &   2039 &   3316 &   3442 \\
    UFBV       &     53 &     97 &     97 \\
    UFDT       &     -- &     -- &   1863 \\
    UFIDL      &     62 &     57 &     57 \\
    UFLIA      &   8377 &   7714 &   7743 \\
    UFLRA      &     20 &     10 &     10 \\
    UFNIA      &   2318 &   2432 &   2457 \\
    \hline
    Total      &  93241 & 114233 & 130705 \\
    \hline
  \end{tabular}}
\end{table}

@@

\begin{table}
  \caption{Wall-clock time limits}
  \label{table:time-limits}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    & \multicolumn{1}{c|}{2015} & \multicolumn{1}{c|}{2016} & \multicolumn{1}{c|}{2017} & \multicolumn{1}{c|}{2018} \\
    \hline
    Main track        & 40~min & 40~min & 20~min\protect\footnotemark & 20~min \\
    Application track & 40~min & 40~min & 40~min\phantom{$^{1.}$} & 40~min \\
    Unsat-core track  &     -- & 40~min & 40~min\phantom{$^{1.}$} & 40~min \\
    \hline
  \end{tabular}
\end{table}
\footnotetext{These job pairs were first run with a time limit of
  10~minutes.  See the text for details.}

@@

\begin{table}
  \caption{Participants (2015--2018)}
  \label{table:participants}
  \centering
  \begin{tabular}{|l|p{11.5cm}|}
    \hline
    Solver & Submitters (Affiliations)\\
    \hline
    ABC~\cite{DBLP:conf/cav/BraytonM10} & Valeriy Balabanov
                        (Mentor Graphics)\\
    Alt-Ergo~\cite{conchon:hal-01960203} & Albin Coquereau
                        (CNRS and University of Paris-Sud)\\
    AProVE~\cite{DBLP:journals/jar/GieslABEFFHOPSS17} & Carsten Fuhs
                        (University College London; Birkbeck, University of London)\\
    Boolector~\cite{DBLP:conf/cav/NiemetzPWB18} & Mathias Preiner
                        (Johannes Kepler University, Stanford University)\\
    COLIBRI~\cite{colibri} & Fran\c{c}ois Bobot
                        (French Alternative Energies and Atomic Energy Commission)\\
    Ctrl-Ergo~\cite{10.1007/978-3-642-31365-3_8} & Mohamed Iguernlala
                        (OCamlPro SAS)\\
    CVC3~\cite{DBLP:conf/cav/BarrettT07} & Kshitij Bansal
                        (New York University)\\
    CVC4~\cite{DBLP:conf/cav/BarrettCDHJKRT11}  & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                        (New York University; Stanford University)\\
    MapleSTP          & Jimmy Liang
                        (University of Waterloo)\\
    MinkeyRink        & Trevor Hansen
                        (University of Melbourne)\\
    OpenSMT2~\cite{DBLP:conf/sat/HyvarinenMAS16} & Matteo Marescotti, Antti Hyv\"arinen
                        (University of Lugano)\\
    ProB~\cite{doi:10.1002/9781119002727.ch14} & Sebastian Krings
                        (University of D\"usseldorf)\\
    Q3B               & Martin Jon\'a\v{s}
                        (Masaryk University)\\
    raSAT~\cite{rasat} & Tung Vu Xuan
                        (Japan Advanced Institute of Science and Technology)\\
    Redlog~\cite{DBLP:journals/cca/Dolzmann097} & Haniel Barbosa
                        (Inria Nancy)\\
    SMT-RAT~\cite{DBLP:conf/sat/CorziliusKJSA15} & Florian Corzilius, Gereon Kremer
                        (RWTH Aachen University)\\
    SMTInterpol~\cite{DBLP:conf/spin/ChristHN12} & J\"urgen Christ
                        (University of Freiburg)\\
    SPASS-SATT         & Martin Bromberger
                        (Max Planck Institute for Informatics)\\
    STP~\cite{ganesh07} & Mate Soos, Trevor Hansen, Norbert Manthey
                        (National University of Singapore; University of Melbourne)\\
    toysmt             & Masahiro Sakai
                        (Toshiba Corporation)\\
    Vampire~\cite{DBLP:conf/cav/KovacsV13} & Giles Reger
                        (University of Manchester)\\
    veriT~\cite{DBLP:conf/cade/BoutonODF09} & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
    XSat~\cite{DBLP:conf/cav/FuS16} & Martin Velez
                        (University of California, Davis)\\
    Yices2~\cite{Dutertre:cav2014} & Bruno Dutertre, Dejan Jovanovi\'c
                        (SRI International)\\
    Z3~\cite{DBLP:conf/tacas/MouraB08} & Christoph Wintersteiger, Aleksandar Zelji\'c
                        (Microsoft Research; Uppsala University)\\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Number of versions submitted for each solver (by year).
    Numbers in square brackets indicate solver versions that were
    participating hors concours.}
  \label{table:participants-history}
  \centering
  \begin{tabular}{|l|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|r@{\,\,}r|}
    \hline
    Solver & \multicolumn{2}{c|}{2015} & \multicolumn{2}{c|}{2016} & \multicolumn{2}{c|}{2017} & \multicolumn{2}{c|}{2018} \\
    \hline
    ABC               &    &      &  2 &      &    &      &    &      \\
    Alt-Ergo          &    &      &    &      &    &      &  1 &      \\
    AProVE            &  1 &      &  1 &      &  1 &      &  1 &      \\
    Boolector         &  3 & [+1] &  2 &      &  2 &      &  2 &      \\
    COLIBRI           &    &      &    &      &  1 &      &  1 &      \\
    Ctrl-Ergo         &    &      &    &      &    &      &  1 &      \\
    CVC3              &  2 &      &    &      &    &      &    &      \\
    CVC4              &  4 &      &  1 & [+1] &  3 &      &  3 & [+1] \\
    MapleSTP          &    &      &  4 &      &    &      &    &      \\
    {[}MathSAT{]}     &    & [+2] &    & [+3] &    & [+3] &    & [+3] \\
    MinkeyRink        &    &      &  1 &      &  1 &      &  2 &      \\
    OpenSMT2          &  2 &      &  1 &      &  1 &      &    & [+1] \\
    ProB              &    &      &  1 &      &    &      &    &      \\
    Q3B               &    &      &  1 &      &  1 &      &  1 &      \\
    raSAT             &  1 &      &  2 &      &    &      &    &      \\
    Redlog            &    &      &    &      &  1 &      &    &      \\
    SMT-RAT           &  2 &      &  1 &      &  1 &      &  2 &      \\
    SMTInterpol       &  1 &      &  1 &      &  1 &      &  1 &      \\
    SPASS-SATT        &    &      &    &      &    &      &  1 &      \\
    STP               &  4 &      &  8 &      &  2 &      &  3 &      \\
    toysmt            &    &      &  1 &      &    &      &    &      \\
    Vampire           &    &      &  2 &      &  1 &      &  1 &      \\
    veriT             &  1 &      &  1 &      &  3 &      &  2 &      \\
    XSat              &    &      &    &      &  1 &      &    &      \\
    Yices2            &  3 &      &  2 &      &  2 &      &  3 &      \\
    Z3                &  2 & [+1] &    & [+1] &    & [+1] &    & [+1] \\
    \hline
    Total             & 26 & [+4] & 32 & [+5] & 22 & [+4] & 25 & [+6] \\
    \hline
  \end{tabular}
\end{table}

>>>>

\usepackage{jsat}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{booktabs}
%\usepackage[pdf]{pstricks}
%\usepackage{pst-tree}

@@

\begin{table}
  \caption{Number of benchmarks and logics in the SMT Library}
  \label{table:smtlib}
  \centering
  \begin{tabular}{r@{\ \ }lrrrr}
    \toprule
                               & & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    \multirow{2}{*}{Non-incremental $\{$} & benchmarks & 196375 & 196114 & 258079 & 336844 \\
                                          & logics     &     40 &     40 &     49 &     51 \\
    \multirow{2}{*}{Incremental $\{$}     & benchmarks &  10019 &  10024 &   6262 &  10167 \\
                                          & logics     &     15 &     15 &     22 &     26 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Number of divisions in each competition track}
  \label{table:divisions}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    & 2015 & 2016 & 2017 & 2018 \\
    \midrule
    Main track        &  40 & 40 & 49 & 50 \\
    Application track &  14 & 14 & 16 & 21 \\
    Unsat-core track  &  -- & 40 & 41 & 44 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Number of benchmarks used in the main track (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.8]{\begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \midrule
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \bottomrule
  \end{tabular}}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the application track (by
    division)}
  \label{table:benchmarks-application-track}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ALIA       &   24 &   24 &   24 &   24 \\
    ANIA       &    3 &    3 &    3 &    3 \\
    AUFNIRA    &   -- &   -- &   -- &  117 \\
    BV         &   -- &   -- &   -- &   17 \\
    LIA        &    6 &    6 &    6 &    6 \\
    QF\_ABV    &   -- &   -- &   -- &   15 \\
    QF\_ALIA   &   44 &   44 &   44 &   44 \\
    QF\_ANIA   &    5 &    5 &    5 &    5 \\
    QF\_AUFBV  &   -- &   -- &   -- &   10 \\
    QF\_AUFLIA &   72 &   72 &   72 &   72 \\
    QF\_BV     &   18 &   18 &   18 &  815 \\
    QF\_BVFP   &   -- &   -- &    2 &    2 \\
    QF\_FP     &   -- &   -- &    2 &    2 \\
    QF\_LIA    &   65 &   69 &   68 &   69 \\
    QF\_LRA    &   10 &   10 &   10 &   10 \\
    QF\_NIA    &   10 &   10 &   10 &   10 \\
    QF\_UFBV   &   -- &   -- &   -- & 2327 \\
    QF\_UFLIA  &  905 &  905 &  780 &  780 \\
    QF\_UFLRA  & 3331 & 3331 & 3056 & 3058 \\
    QF\_UFNIA  &    1 &    1 &    1 &    1 \\
    UFLRA      & 5358 & 5358 & 1870 & 1870 \\
    \midrule
    Total      & 9852 & 9856 & 5971 & 9257 \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Number of benchmarks used in the unsat-core track (by
    division)}
  \label{table:benchmarks-unsat-core-track}
  \centering
  \scalebox{1}[.91]{\begin{tabular}{lrrr}
    \toprule
    Division & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ALIA       &     41 &     41 &     41 \\
    AUFBVDTLIA &     -- &     -- &     25 \\
    AUFLIA     &      3 &      3 &      3 \\
    AUFLIRA    &  19749 &  19771 &  19771 \\
    AUFNIRA    &   1046 &   1050 &   1053 \\
    BV         &     56 &     94 &   4937 \\
    LIA        &    191 &    233 &    233 \\
    LRA        &    319 &   1106 &   1539 \\
    NIA        &      3 &      4 &      4 \\
    NRA        &   3788 &   3801 &   3801 \\
    QF\_ABV    &   4644 &   4673 &   4677 \\
    QF\_ABVFP  &     -- &   3934 &   3934 \\
    QF\_ALIA   &     80 &     80 &     80 \\
    QF\_ANIA   &      8 &      8 &      8 \\
    QF\_AUFBV  &     31 &     25 &     25 \\
    QF\_AUFLIA &    516 &    516 &    516 \\
    QF\_AUFNIA &     15 &     12 &     12 \\
    QF\_AX     &    279 &    279 &    279 \\
    QF\_BV     &  17172 &  23732 &  25700 \\
    QF\_BVFP   &      6 &   3174 &   3174 \\
    QF\_DT     &     -- &     -- &   4422 \\
    QF\_FP     &  17213 &  20028 &  20026 \\
    QF\_IDL    &    816 &    816 &    816 \\
    QF\_LIA    &   2840 &   2844 &   3019 \\
    QF\_LIRA   &      5 &      5 &      5 \\
    QF\_LRA    &    633 &    671 &    683 \\
    QF\_NIA    &    316 &   3130 &   4842 \\
    QF\_NIRA   &      2 &      2 &      2 \\
    QF\_NRA    &   4948 &   5296 &   5357 \\
    QF\_RDL    &    113 &    113 &    113 \\
    QF\_UF     &   4100 &   4101 &   4330 \\
    QF\_UFBV   &     31 &     31 &    575 \\
    QF\_UFIDL  &    335 &    322 &    322 \\
    QF\_UFLIA  &    195 &    183 &    183 \\
    QF\_UFLRA  &    853 &    511 &    511 \\
    QF\_UFNIA  &      7 &      7 &      7 \\
    QF\_UFNRA  &     18 &     11 &     11 \\
    UF         &   2039 &   3316 &   3442 \\
    UFBV       &     53 &     97 &     97 \\
    UFDT       &     -- &     -- &   1863 \\
    UFIDL      &     62 &     57 &     57 \\
    UFLIA      &   8377 &   7714 &   7743 \\
    UFLRA      &     20 &     10 &     10 \\
    UFNIA      &   2318 &   2432 &   2457 \\
    \midrule
    Total      &  93241 & 114233 & 130705 \\
    \bottomrule
  \end{tabular}}
\end{table}

@@

\begin{table}
  \caption{Wall-clock time limits (in minutes)}
  \label{table:time-limits}
  \centering
  \begin{tabular}{lcccc}
    \toprule
    & 2015 & 2016 & 2017 & 2018 \\
    \midrule
    Main track        & 40 & 40 & 20\protect\footnotemark & 20 \\
    Application track & 40 & 40 & 40\phantom{$^{1.}$}      & 40 \\
    Unsat-core track  & -- & 40 & 40\phantom{$^{1.}$}      & 40 \\
    \bottomrule
  \end{tabular}
\end{table}
\footnotetext{These job pairs were first run with a time limit of
  10~minutes.  See the text for details.}

@@

\begin{table}
  \caption{Participants (2015--2018)}
  \label{table:participants}
  \centering
  \begin{tabular}{lp{11.5cm}}
    \toprule
    Solver & Submitters (Affiliations)\\
    \midrule
    ABC~\cite{DBLP:conf/cav/BraytonM10} & Valeriy Balabanov
                        (Mentor Graphics)\\
    Alt-Ergo~\cite{conchon:hal-01960203} & Albin Coquereau
                        (CNRS and University of Paris-Sud)\\
    AProVE~\cite{DBLP:journals/jar/GieslABEFFHOPSS17} & Carsten Fuhs
                        (University College London; Birkbeck, University of London)\\
    Boolector~\cite{DBLP:conf/cav/NiemetzPWB18} & Mathias Preiner
                        (Johannes Kepler University, Stanford University)\\
    COLIBRI~\cite{colibri} & Fran\c{c}ois Bobot
                        (French Alternative Energies and Atomic Energy Commission)\\
    Ctrl-Ergo~\cite{10.1007/978-3-642-31365-3_8} & Mohamed Iguernlala
                        (OCamlPro SAS)\\
    CVC3~\cite{DBLP:conf/cav/BarrettT07} & Kshitij Bansal
                        (New York University)\\
    CVC4~\cite{DBLP:conf/cav/BarrettCDHJKRT11}  & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                        (New York University; Stanford University)\\
    MapleSTP          & Jimmy Liang
                        (University of Waterloo)\\
    MinkeyRink        & Trevor Hansen
                        (University of Melbourne)\\
    OpenSMT2~\cite{DBLP:conf/sat/HyvarinenMAS16} & Matteo Marescotti, Antti Hyv\"arinen
                        (University of Lugano)\\
    ProB~\cite{doi:10.1002/9781119002727.ch14} & Sebastian Krings
                        (University of D\"usseldorf)\\
    Q3B               & Martin Jon\'a\v{s}
                        (Masaryk University)\\
    raSAT~\cite{rasat} & Tung Vu Xuan
                        (Japan Advanced Institute of Science and Technology)\\
    Redlog~\cite{DBLP:journals/cca/Dolzmann097} & Haniel Barbosa
                        (Inria Nancy)\\
    SMT-RAT~\cite{DBLP:conf/sat/CorziliusKJSA15} & Florian Corzilius, Gereon Kremer
                        (RWTH Aachen University)\\
    SMTInterpol~\cite{DBLP:conf/spin/ChristHN12} & J\"urgen Christ
                        (University of Freiburg)\\
    SPASS-SATT         & Martin Bromberger
                        (Max Planck Institute for Informatics)\\
    STP~\cite{ganesh07} & Mate Soos, Trevor Hansen, Norbert Manthey
                        (National University of Singapore; University of Melbourne)\\
    toysmt             & Masahiro Sakai
                        (Toshiba Corporation)\\
    Vampire~\cite{DBLP:conf/cav/KovacsV13} & Giles Reger
                        (University of Manchester)\\
    veriT~\cite{DBLP:conf/cade/BoutonODF09} & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
    XSat~\cite{DBLP:conf/cav/FuS16} & Martin Velez
                        (University of California, Davis)\\
    Yices2~\cite{Dutertre:cav2014} & Bruno Dutertre, Dejan Jovanovi\'c
                        (SRI International)\\
    Z3~\cite{DBLP:conf/tacas/MouraB08} & Christoph Wintersteiger, Aleksandar Zelji\'c
                        (Microsoft Research; Uppsala University)\\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Number of versions submitted for each solver (by year).
    Numbers in square brackets indicate solver versions that were
    participating hors concours.}
  \label{table:participants-history}
  \centering
  \begin{tabular}{lr@{\,\,}rr@{\,\,}rr@{\,\,}rr@{\,\,}r}
    \toprule
    Solver & \multicolumn{2}{c}{2015} & \multicolumn{2}{c}{2016} & \multicolumn{2}{c}{2017} & \multicolumn{2}{c}{2018} \\
    \midrule
    ABC               &    &      &  2 &      &    &      &    &      \\
    Alt-Ergo          &    &      &    &      &    &      &  1 &      \\
    AProVE            &  1 &      &  1 &      &  1 &      &  1 &      \\
    Boolector         &  3 & [+1] &  2 &      &  2 &      &  2 &      \\
    COLIBRI           &    &      &    &      &  1 &      &  1 &      \\
    Ctrl-Ergo         &    &      &    &      &    &      &  1 &      \\
    CVC3              &  2 &      &    &      &    &      &    &      \\
    CVC4              &  4 &      &  1 & [+1] &  3 &      &  3 & [+1] \\
    MapleSTP          &    &      &  4 &      &    &      &    &      \\
    {[}MathSAT{]}     &    & [+2] &    & [+3] &    & [+3] &    & [+3] \\
    MinkeyRink        &    &      &  1 &      &  1 &      &  2 &      \\
    OpenSMT2          &  2 &      &  1 &      &  1 &      &    & [+1] \\
    ProB              &    &      &  1 &      &    &      &    &      \\
    Q3B               &    &      &  1 &      &  1 &      &  1 &      \\
    raSAT             &  1 &      &  2 &      &    &      &    &      \\
    Redlog            &    &      &    &      &  1 &      &    &      \\
    SMT-RAT           &  2 &      &  1 &      &  1 &      &  2 &      \\
    SMTInterpol       &  1 &      &  1 &      &  1 &      &  1 &      \\
    SPASS-SATT        &    &      &    &      &    &      &  1 &      \\
    STP               &  4 &      &  8 &      &  2 &      &  3 &      \\
    toysmt            &    &      &  1 &      &    &      &    &      \\
    Vampire           &    &      &  2 &      &  1 &      &  1 &      \\
    veriT             &  1 &      &  1 &      &  3 &      &  2 &      \\
    XSat              &    &      &    &      &  1 &      &    &      \\
    Yices2            &  3 &      &  2 &      &  2 &      &  3 &      \\
    Z3                &  2 & [+1] &    & [+1] &    & [+1] &    & [+1] \\
    \midrule
    Total             & 26 & [+4] & 32 & [+5] & 22 & [+4] & 25 & [+6] \\
    \bottomrule
  \end{tabular}
\end{table}
